Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-10-30 Thesis/chapter/060-results-material.tex
add appendix

Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate, steel, and 
the substrate with ten layers of double concentrated solution (experiment number 6113, see \td{appendix}).
In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108).
The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
%In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
%The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
%This wideness is is due to polycrystalline form of the material which is expected 
%due to the sol-gel creation process and multiple applications of layers. 
%Nonetheless, the \gls{xrd} spectra shows clearly that the produced layer is \gls{zro}.

>>>>

Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate, steel, and 
the substrate with ten layers of double concentrated solution (experiment number 6113, see Appendix \ref{sec:app-emma}).
In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108).
The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
%In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
%The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
%This wideness is is due to polycrystalline form of the material which is expected 
%due to the sol-gel creation process and multiple applications of layers. 
%Nonetheless, the \gls{xrd} spectra shows clearly that the produced layer is \gls{zro}.

### 2022-10-30 Thesis/chapter/061-results-emma.tex
post-emma bad first draft
minor change results
good draft results materials/pre-opt
add appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{all samples}
%\input{chapter/emma.table.tex}
A total of 30 recipes have been investigated in 
five iterations of the algorithm ($t = 0, \dots,4$). 
%The best recipe identified by the EMMA algorithm is as follows: 
The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The calcinatino heating $v_{cal}$ rate has been predicted perfectly 
\td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
The number of layers $\lambda$ on the other hand was predicted poorly 
even though the conversion factor wsa 1 and the prediction function dependent on $\lambda$.

@@

\begin{figure}
    \centering
    \begin{subfigure}{.45\textwidth}
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
        \caption{emma G gen } \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
        \caption{emma phd gen} \label{fig:emma-phd-gen}
    \end{subfigure}
    \caption{emma gen} \label{fig:emma-gen}
\end{figure}

@@

\begin{table}[h]
	\centering
    \caption{Global best per generation}
	\label{tab:emma-Gb}
	\begin{tabular}{cccccccc}
        \hline\hline
    generation  &enr &conc &layr &vDOC &TDOC &vCal &TCal\\
        \hline
     1   &1       &2    &4   &10   &40  &120  &300\\
     2   &5       &2    &6   &10   &40  &120  &300\\
     3   &2947    &4    &6   &16   &80 &1080  &300\\
     4   &2405    &2    &6   &10   &40 &1080  &300\\
     5   &13      &2   &10   &10   &40  &120  &300\\
    \hline\hline
	\end{tabular}
\begin{tabular}{cccccc}
    \hline\hline
enr     &1st gen     &2nd gen        &3rd gen        &4th gen        &5th gen\\
    \hline
1       &1.214185    &       &       &       &38.7962       \\
5       &       &4.196626       &       &       &25.47335       \\
2947    &       &       &10.9594    &       &10.9594       \\
2405    &       &       &       &20.04962   &25.47335       \\
13      &       &       &       &       &24.87178   \\
    \hline\hline
\end{tabular}
\end{table}

@@

%\iffalse
\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{Pics/stats/G-t.png}
    \caption{conductivity G [a.u.] against sample number (is this even correct?)}
    \label{fig:G-t}
\end{figure}

\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
\td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
\url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
%\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{what is best}
\begin{align}
    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
    \label{eq:emma}
\end{align}
%what was the best result? For each particle there is best and global best. 
https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%\subsubsection{all samples}
A total of 30 recipes (see \ref{sec:app-emma}) have been investigated in 
five iterations of the algorithm ($t = 0, \dots, 4$). 
%The best recipe identified by the EMMA algorithm is as follows: 
The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The calcination heating $v_{cal}$ rate has been predicted perfectly 
\td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
The number of layers $\lambda$ on the other hand was predicted poorly 
even though the conversion factor wsa 1 and the prediction function dependent on $\lambda$.

@@

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
        \caption{emma G gen } \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
        \caption{emma phd gen} \label{fig:emma-phd-gen}
    \end{subfigure}
    \caption{emma gen} \label{fig:emma-gen}
\end{figure}

@@

\begin{table}[htb]
	\centering
    \caption{Global best per generation}
	\label{tab:emma-Gb}
	\begin{tabular}{cccccccc}
        \hline\hline
    generation  &enr &conc &layr &vDOC &TDOC &vCal &TCal\\
        \hline
     1   &1       &2    &4   &10   &40  &120  &300\\
     2   &5       &2    &6   &10   &40  &120  &300\\
     3   &2947    &4    &6   &16   &80 &1080  &300\\
     4   &2405    &2    &6   &10   &40 &1080  &300\\
     5   &13      &2   &10   &10   &40  &120  &300\\
    \hline\hline
	\end{tabular}
\begin{tabular}{cccccc}
    \hline\hline
enr     &1st gen     &2nd gen        &3rd gen        &4th gen        &5th gen\\
    \hline
1       &1.214185    &       &       &       &38.7962       \\
5       &       &4.196626       &       &       &25.47335       \\
2947    &       &       &10.9594    &       &10.9594       \\
2405    &       &       &       &20.04962   &25.47335       \\
13      &       &       &       &       &24.87178   \\
    \hline\hline
\end{tabular}
\end{table}

@@

\iffalse
\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{Pics/stats/G-t.png}
    \caption{conductivity G [a.u.] against sample number (is this even correct?)}
    \label{fig:G-t}
\end{figure}

\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
\td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
\url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{what is best}
\begin{align}
    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
    \label{eq:emma}
\end{align}
%what was the best result? For each particle there is best and global best.

@@

\td{look at emma papers}
